A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
abstract tweaks

The photometry from the \KT\ extension of NASA's \kepler\ mission is
afflicted by systematic effects caused by the relative imprecision of the
telescope pointing, and possibly other spacecraft effects.
We present a method for searching these light curves for evidence of
exoplanets by simultaneously fitting for these systematics and the
transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to
discover transit signals in the existing dataset.
We apply this method to the full Campaign 1 dataset and report a list of XXX
planet candidates transiting YYY stars.
We also present a list of probably astrophysical false positives, and
the results of some follow-up spectroscopic data on a few of the
planet candidates
The most interesting systems are JJJ and HHH.

>>>>

The photometry from the \KT\ extension of NASA's \kepler\ mission is
afflicted by systematic effects caused by the relative imprecision of the
telescope pointing, and possibly other spacecraft effects.
We present a method for searching these light curves for evidence of
exoplanets by simultaneously fitting for these systematics and the
transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to
discover transit signals in the existing dataset.
We apply this method to the full Campaign 1 dataset and report a list of XXX
planet candidates transiting YYY stars.
For all planet candidates, we present posterior distributions on the 
properties of each system based strictly on the transit observables.
We also present a list of ZZZ candidate eclipsing binary systems.
